---
title: "Data_mgmt_project"
author: "ER and SL"
format: html
---

```{r}
here::i_am("Data_mgmt_Projet.Rproj")
library(here)
library(ggplot2)
library(dplyr)
library(vroom)
library(tidyr)
```

### Data Loading 
Data files are small yet numerous, fortunately, there are only so many ways organizations can name countries so joining the files is not too challenging.
```{r}
Survival_Rate <- vroom(here("New_Data/Survival_Rate.csv"))
Share_Studs_Priv <- vroom(here("New_Data/Share_Priv_lowsec.csv"))
Pop_Density <- vroom(here("New_Data/Reworked_Density.csv"))
Enrolment <- vroom(here("New_Data/Tot_Enrol_Rate_Lowsec.csv"))

Start_Yr <- vroom(here("New_Data/Start_Month_Acad.csv"))
End_Yr <- vroom(here("New_Data/End_Month_Acad.csv"))

Gov_Exp <- vroom(here("New_Data/Gov_Exp_GDP.csv"))

MeanSchooling <- vroom(here("New_Data/Mean_Yrs_Schooling.csv"))
EntranceAge <- vroom(here("New_Data/Entrance_Age.csv"))

```

Notes for later :
- When UNESCO data are aggregated in regional form they don't have a name in character but a number, so it should be easy to rid or separate with a is.number or something of that kind
- Some of the data, notably Illiteracy seem to have different indicators name so we need to ensure that it is the same thing or else separate them in different parts

Due to UNESCO website being fucked up I cannot select the 2000 time period when I select only a few years. So for now I provide the 2009 and 2018 data, with for some data a 3 year range that we could mean, in case there are no data for 2009 or 2018 but some data before or after

- Most of the data has a 'value' to show the value, problem is we would end up with a whole lot of 'values' so need to rename all this probably at the end of each datasets treatment, right before joining everything
- Some variable are duplicated(Share_Studs_Priv has twice Time as well as ALL the UNESCO data), we will need to rid of them
- Might be good to quickly turn Start and End of Year data sets into one so we can acquire the info we want out of it, namely the duration of a school year.

### Some testing processes


